Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-18 chap-intro.tex
Revise chap-operationally for other proof
Also revise a few things internally.
Add TODO to general intro
Nits

@@

Furthermore, \cref{part:caching} comes from a new, unpublished
manuscript~\citep*{Giarrusso2018Static}. I
designed the overall approach, the transformation and the case study on
sequences and nested loops. Proofs were done in collaboration with Yann
Régis-Gianas: most of the actual mechanization work is his, though I contributed significantly to the
correctness proof for ILC. Philipp Schuster contributed to the evaluation,
devising language plugins for bags and maps.

>>>>

%\Cref{part:ch-aosd13} makes the following contributions:
\pg{TODO:contributions of other parts.}

@@

Furthermore, \cref{ch:cts} comes from a recently submitted
manuscript~\citep*{Giarrusso2018Static}. I
designed the overall approach, the transformation and the case study on
sequences and nested loops. Proofs were done in collaboration with Yann
Régis-Gianas: most of the actual mechanization work is his, though I contributed significantly to the
correctness proof for ILC. Philipp Schuster contributed to the evaluation,
devising language plugins for bags and maps in collaboration with me.
